\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-11 doc/sui14/iteration3.tex
task performance for iteration 3

The users had strong preferences for the new method of refinement. On a scale
from 1-7, 1 being the least mental effort and 7 being the most mental effort
users rated the old technique 4.25 and the new technique 2 on average. 100\%
indicated a preference for head movement to list navigation. One user
referenced the issue of naming targets that the list necessitates, preferring
the experience of \studyquote{matching visual cues rather than numbers}.
Another participant remarked that it \studyquote{just made more sense} and was
a \studyquote{more natural way for demonstrating intentionality}. The users
preferred the new mapping in relation to the whole environment: \studyquote{it
leveraged the spatial sense that I already had just by using the system}. They
were also delighted to avoid list navigation, which they now called
\studyquote{difficult} and \studyquote{painful}.

>>>>

The users had strong preferences for the new method of refinement.
\changes{Though we lack formal data to evaluate the performance of
this method, from our observeation during the experiments, we found
that each trial became much easier than previous iterations. We
conducted a survey to collect qualitative feedback after the
experiement.} On a scale from 1-7, 1 being the least mental effort and
7 being the most mental effort users rated the old technique 4.25 and
the new technique 2 on average. 100\% indicated a preference for head
movement to list navigation. One user referenced the issue of naming
targets that the list necessitates, preferring the experience of
\studyquote{matching visual cues rather than numbers}.  Another
participant remarked that it \studyquote{just made more sense} and was
a \studyquote{more natural way for demonstrating intentionality}. The
users preferred the new mapping in relation to the whole environment:
\studyquote{it leveraged the spatial sense that I already had just by
using the system}. They were also delighted to avoid list navigation,
which they now called \studyquote{difficult} and \studyquote{painful}.
